### 2023-05-10 conference-paper/main.tex
Intro and tables fixed

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{siunitx}
\sisetup{group-separator = {,}}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{float}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{longtable,tabularx}
\usepackage{placeins}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{latexsym}
\usepackage{multicol}
\usepackage{subcaption}
\usepackage[sort&compress,numbers]{natbib} % For bibtex \citet, \citep
\usepackage{hypernat} % To get natbib to play nicely with hyperref
\usepackage{doi} % For getting hyperlinked DOI in the references

@@

% [x] TODO: AL-PA, Consider changing the title to "Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization"
\title{Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization} % change
\author{Peter N. Atma\footnote{MSE Student, Department of Aerospace Engineering, AIAA Student Member}}
\author{Andrew H~.R.~Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
\author{Joaquim R.~R.~A.~Martins\footnote{Professor, Department of Aerospace Engineering, AIAA Fellow}}
\affil{University of Michigan, Ann Arbor, MI, 48109}

@@

% ==================================================
%	Abstract
% ==================================================
\begin{abstract}
  Advances in commercial propulsion technology led to the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
  Current trends suggest that geared ultra high bypass ratio turbofans are the next generation of commercial propulsion systems.
  Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
  Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
  In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
  We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
  The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
  % Advances in commercial propulsion technology are pushing the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
  Current trends suggest that geared ultra high bypass ratio turbofans are the next generation of commercial propulsion systems.
  These engines pose a difficult design problem due to high internal temperatures, large overall pressure ratios, and increasingly smaller cores.
  Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
  Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
  In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
  We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
  The results quantify the design space for next-generation propulsion concepts that can benefit from hydrogen fuel's advantageous properties to reduce emissions and improve performance.
  % The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
\end{abstract}

@@

% NOTE: AL-PA, I turned this into a subfigure to save some space
\begin{figure}[hbt!]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \includegraphics[width=\textwidth]{injector.pdf}
    \caption{
      Water from the extractor is simply injected into the core flow upstream of the high-pressure compressor.
    }
    \label{fig:injector}
  \end{subfigure}
  \hspace{2pt}
  \begin{subfigure}[t]{0.49\textwidth}
    \includegraphics[width=\textwidth]{extractor.pdf}
    \caption{
      We extract a fraction of the moles of water from the out flow of duct 5.
      The extracted water is routed back upstream to the injector and the rest is exhausted out the nozzle.
    }
    \label{fig:extractor}
  \end{subfigure}
  % [x] TODO: AL-PA, Might want to add a bit more to this caption if you think it's necessary.
  \caption{Injector (left) and extractor(right) diagrams that show the inputs and output streams of each component.
    The inputs and outputs show which flow values are used to compute the amount of recirculated water.}
  \label{fig:extract_inject}
\end{figure}

The water extractor model diverts a fraction of a specific species from one flow path to another.
The CEA solver calculates the inflow composition and the extractor separates a specific species based on a mass fraction input.
The composition of the core stream is updated to represent the remaining mixture after the extractor model removes the species from the incoming flow.
We then solve for the thermodynamic state and flow path areas at the outflow of both extractor streams.
A simple schematic of the extractor is shown in Figure~\ref{fig:extractor} where \ce{Y_{\ce{H2O}}} is the mole fraction of water molecules and \ce{X_{\ce{H2O}}} is the fraction of water that is recovered from the core stream.
We connect one outflow stream of the extractor to the inflow stream of the injector to complete the water recirculation system.

@@

% [x] TODO: AL-PA, Why are some of the fist words in the descriptions capitalized but not others?  I think this should be consistent.
% [x] TODO: AL-PA, Change the lower heating value references to footnotes. i.e \footnote{\url{...}}
\begin{table}[hbt!]
  \centering
  \caption{
    N+3 model fuel properties.
    The lower heating values are given for each fuel used to compute TSEC.}
  \begin{tabular}{r r r l}
    \hline
    Parameter              & Value   & Units        & Description                                                                                                            \\
    \hline                                                                                                                                                                   \\
    $\rm{LHV}_{\rm{JetA}}$ & 18564.0 & \si{BTU/lbm} & Lower heating value of Jet-A \footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
    $\rm{LHV}_{\rm{H2}}$   & 51591.0 & \si{BTU/lbm} & Lower heating value of H2 \footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
    \hline
  \end{tabular}
  \label{fuel_props}
\end{table}

@@

\begin{equation}
  V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}}
  \label{eq:vratio}
\end{equation}
where $V_\text{ideal}$ is the ideal nozzle exit velocity and $C_v$ is the nozzle velocity coefficient that accounts for non-ideal effects.
The final design variable is the water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$).
% [x] TODO: AL-PA, optimizing for fuel burn subject to net thrust constraint...
% [x] TODO: AL-PA, this isn't the only reason we consider just the water recovery at cruise.  It's also the longest flight segment and contributes the most to long-term performance.
We only include the water recovery fraction at cruise because it has the largest impact on the fuel mass flow rate objective function.
Additionally, the CRZ operating condition is the longest flight segment and contributes the most to long-term engine performance.
The range for each design variable and the associated units are shown in Table~\ref{tab:dv_table}.
% We add the water recovery fraction only at the CRZ point as a design variable since we are optimizing $\dot{m}_{\rm{fuel,CRZ}}$.

@@

% [x] TODO: AL-PA, Define the T4 ratio with an equation and reference the equation in the table
% [x] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
% [x] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
% [x] TODO: PA-PA, explain variable ranges
\begin{table}[hbt!]
  \centering
  \caption{
    Multipoint optimization problem definition.
    The objective function is the thrust specific energy consumption at the cruise condition.
    The constraints are net thrust and engine diameter constraint at the design point, TOC.
  }
  \small
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{r l l r l}
    \toprule
                    & Variable/Function              & Description                                                              & Units          & Quantity \\
    \hline
    minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Fuel flow rate at CRZ                                                    & \si{lbm/s}     & 1        \\
                    &                                &                                                                          &                &          \\
    with respect to & $X_{\rm{H_2O,CRZ}}$            & Water recovery mass fraction at CRZ                                      & -              & 1        \\
                    & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                                                   & -              & 1        \\
                    & $\rm{PR}_{\rm{LPC,TOC}}$       & TOC low-pressure compressor pressure ratio                               & -              & 1        \\
                    & $\rm{OPR}_{\rm{TOC}}$          & TOC overall pressure ratio                                               & -              & 1        \\
                    & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \si{\degree R} & 1        \\
                    & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation~\eqref{t4ratio})                  & -              & 1        \\
                    & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation~\eqref{eq:vratio}) & -              & 1        \\
    \cline{3-5}
                    &                                & Total                                                                    &                & 7        \\
                    &                                &                                                                          &                &          \\
    subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                                 & \si{lbf}       & 1        \\
                    & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                     & \si{inch^2}    & 1        \\
    \cline{3-5}
                    &                                & Total                                                                    &                & 2        \\
    \bottomrule
  \end{tabular}
  \label{tab:opt_problem}
\end{table}

@@

% Thrust splits
% [x] TODO: PA-PA: Add thrust splits for each opt
% [x] TODO: AL-PA: I think this should be showing gross thrust from the fan divided by gross thrust from the core.
%                  The idea here is to show percentages of thrust generated by fan/core and how that changes with water recovery.
\begin{table}[hbt!]
  \centering
  \caption{Thrust breakdown for each flight operating condition.
    The net thrust, gross thrust, and ram drag are shown for each optimization result.
  }
  \small
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{r l l l l l}
    Point & Thrust Fraction & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
    \toprule
    TOC   & Core            & 6.47\%    & 6.05\%    & 5.95\%  & 5.47\%  \\
          & Bypass          & 93.53\%   & 93.95\%   & 94.05\% & 94.53\% \\
    \hline
    RTO   & Core            & 6.31\%    & 5.87\%    & 5.77\%  & 5.26\%  \\
          & Bypass          & 93.69\%   & 94.13\%   & 94.23\% & 94.74\% \\
    \hline
    SLS   & Core            & 6.11\%    & 5.68\%    & 5.58\%  & 5.09\%  \\
          & Bypass          & 93.89\%   & 94.32\%   & 94.42\% & 94.91\% \\
    \hline
    CRZ   & Core            & 6.02\%    & 5.42\%    & 5.53\%  & 4.71\%  \\
          & Bypass          & 93.98\%   & 94.58\%   & 94.47\% & 95.29\% \\
    \bottomrule
  \end{tabular}
  \label{tab:thrust}
\end{table}

@@

The TSEC improvement at CRZ due to water recovery for both fuels is shown on a bar chart in Figure~\ref{fig:barchart}.
Water recovery improves the TSEC approximately 5\% for both Jet-A and hydrogen fueled cycles.
% We see an improvement greater than 5\% at CRZ for TSEC for both fuels.
% [x] TODO: AL-PA, This is a good point, but maybe combine with the paragraph after the figure?
Most of the design variables for the optimal designs with and without water recovery vary only slightly for both fuels.
This suggests that the water recovery system accounts for a majority of the efficiency improvements.
Achieving a 5\% reduction in TSEC represents a large fuel savings over the lifecycle of an engine.
% This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
% [x] TODO: AL-PA, Add a sentence that introduces this citation and paraphrases the claim.  Then relate it to your findings.
As~\citeauthor{Strom2002} point out, a hydrogen-fueled engine would have close to 3 times more water in the exhaust than a similar Jet-A fueled counterpart.
% [x] TODO: AL-PA, I think we need to add some numbers here for the mass flow rate of water for jet-a and hydrogen to help this claim.
The engine designs with water recovery showed that there was about 2.38\si{lbm/s} and 1.08\si{lbm/s} of water in the core stream for \ce{H2} and Jet-A, respectively
% Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
Hydrogen combustion offers an immediate reduction in emissions and produces more water in the exhaust stream.
With an advanced water recovery system, we can achieve better TSEC with hydrogen fuel than Jet-A.
To make hydrogen fueled engines a reality, we need to take advantage of the additional benefits of hydrogen combustion.
\subsection{Condenser Design Space Study}
\label{sub:dpqp_sweep}
% [x] TODO: AL-PA, I would emphasize that we did this sweep to explore the design space following our optimization results.
%                  Might be worth moving this into a new subsection.
% [x] TODO: AL-PA, This study wasn't motivated by a lack of literature, we want to explore the potential design space for the technology we just proposed and analyzed.
The efficiency improvement gained from water recirculation warrant a design space study for potential condenser technology.
Companies that are developing engines with water recirculation suggest that hydrogen can be used to as the heat sink for a water condenser~\cite{arpa-e_2021}.
We consider a condenser designed to fit inside the exhaust stream of a hydrogen-fueled turbofan engine.
The trade space for a condenser in the exhaust stream depends on the pressure loss and water recovery capability.
% A low pressure loss condenser would need to be developed for the water recirculation loop to be implemented.
% [x] TODO: AL-PA, dPqP is the relative total pressure loss not just a "pressure loss"

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{siunitx}
\sisetup{group-separator = {,}}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{float}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{longtable,tabularx}
\usepackage{placeins}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{latexsym}
\usepackage{multicol}
\usepackage{subcaption}
\usepackage[sort&compress,numbers]{natbib} % For bibtex \citet, \citep
\usepackage{hypernat} % To get natbib to play nicely with hyperref
\usepackage{doi} % For getting hyperlinked DOI in the references
\usepackage{hyperref}

@@

% [x] TODO: AL-PA, Consider changing the title to "Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization"
\title{Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization} % change
\author{Peter N.~Atma\footnote{MSE Student, Department of Aerospace Engineering, AIAA Student Member}}
\author{Andrew H~.R.~Lamkin\footnote{Ph.D.~Candidate, Department of Aerospace Engineering, AIAA Student Member}}
\author{Joaquim R.~R.~A.~Martins\footnote{Professor, Department of Aerospace Engineering, AIAA Fellow}}
\affil{University of Michigan, Ann Arbor, MI, 48109}

@@

% ==================================================
%	Abstract
% ==================================================
\begin{abstract}
  Advances in commercial propulsion technology led to the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
  Current trends suggest that geared ultra high bypass ratio turbofans are the next generation of commercial propulsion systems.
  Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
  Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
  In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
  We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
  The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
  % Advances in commercial propulsion technology are pushing the development of efficient high bypass ratio turbofan engines with larger overall pressure ratios and internal temperatures.
  % Current trends suggest that geared ultra high bypass ratio turbofans are the next generation of commercial propulsion systems.
  % These engines pose a difficult design problem due to high internal temperatures, large overall pressure ratios, and increasingly smaller cores.
  % Furthermore, the emphasis on decreasing emissions has driven the exploration of hydrogen-powered aircraft, adding to the already challenging design space.
  % Carrying and burning hydrogen introduces complexity and weight penalties that we must offset using the fuel's thermodynamic and chemical properties.
  % In this study, we create a closed-loop water recirculation system with a zero-dimensional thermodynamic model and compare the benefits between Jet-A and hydrogen fuels.
  % We perform a gradient-based optimization parameter sweep to explore the trade-offs between performance and emissions using both fuels with water recirculation.
  % The results quantify the design space for next-generation propulsion concepts that can benefit from hydrogen fuel's advantageous properties to reduce emissions and improve performance.
  % The results quantify the design space for next-generation propulsion concepts that can take advantage of hydrogen fuel's advantageous thermodynamic properties to reduce emissions and improve performance.
\end{abstract}

@@

% NOTE: AL-PA, I turned this into a subfigure to save some space
\begin{figure}[hbt!]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \includegraphics[width=\textwidth]{injector.pdf}
    \caption{
      Water from the extractor is simply injected into the core flow upstream of the high-pressure compressor.
    }
    \label{fig:injector}
  \end{subfigure}
  \hspace{2pt}
  \begin{subfigure}[t]{0.49\textwidth}
    \includegraphics[width=\textwidth]{extractor.pdf}
    \caption{
      We extract a fraction of the mass flow of water determined by the molar composition.
      The extracted water is routed from duct 5 back upstream to the injector and the rest is exhausted out the nozzle.
    }
    \label{fig:extractor}
  \end{subfigure}
  % [x] TODO: AL-PA, Might want to add a bit more to this caption if you think it's necessary.
  \caption{Injector (left) and extractor(right) diagrams that show the inputs and output streams of each component.
    The inputs and outputs show which flow values are used to compute the amount of recirculated water.}
  \label{fig:extract_inject}
\end{figure}

The water extractor model diverts a fraction of a specific species from one flow path to another.
The CEA solver calculates the inflow composition and the extractor separates a specific species based on a mass fraction input.
The composition of the core stream is updated to represent the remaining mixture after the extractor model removes the species from the incoming flow.
We then solve for the thermodynamic state and flow path areas at the outflow of both extractor streams.
A simple schematic of the extractor is shown in Figure~\ref{fig:extractor} where \ce{Y_{\ce{H2O}}} is the mole fraction of water molecules and \ce{X_{\ce{H2O}}} is the mass fraction of water that is recovered from the core stream.
We connect one outflow stream of the extractor to the inflow stream of the injector to complete the water recirculation system.

@@

% [x] TODO: AL-PA, Why are some of the fist words in the descriptions capitalized but not others?  I think this should be consistent.
% [x] TODO: AL-PA, Change the lower heating value references to footnotes. i.e \footnote{\url{...}}
\begin{table}[hbt!]
  \centering
  \caption{
    N+3 model fuel properties.
    The lower heating values are given for each fuel used to compute TSEC.}
  \begin{tabular}{r r r l}
    \hline
    Parameter              & Value & Units        & Description                                                                                                            \\
    \hline
    $\rm{LHV}_{\rm{JetA}}$ & 18564 & \si{BTU/lbm} & Lower heating value of Jet-A~\footnote{\url{https://www.smartcockpit.com/docs/Jet_Fuel_Characteristics.pdf}}           \\
    $\rm{LHV}_{\rm{H2}}$   & 51591 & \si{BTU/lbm} & Lower heating value of H2~\footnote{\url{https://www.engineeringtoolbox.com/fuels-higher-calorific-values-d_169.html}} \\
    \hline
  \end{tabular}
  \label{fuel_props}
\end{table}

@@

\begin{equation}
  V_{\rm{ratio}} = \frac{V_{\rm{core,ideal}}C_{v,\rm{core}}}{V_{\rm{bypass,ideal}}C_{v,\rm{bypass}}}
  \label{eq:vratio}
\end{equation}
where $V_\text{ideal}$ is the ideal nozzle exit velocity and $C_v$ is the nozzle velocity coefficient that accounts for non-ideal nozzle effects.
The final design variable is the water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$).
% [x] TODO: AL-PA, optimizing for fuel burn subject to net thrust constraint...
% [x] TODO: AL-PA, this isn't the only reason we consider just the water recovery at cruise.  It's also the longest flight segment and contributes the most to long-term performance.
We only include the water recovery fraction at cruise because it has the largest impact on the fuel mass flow rate objective function.
Additionally, the CRZ operating condition is the longest flight segment and contributes the most to long-term engine performance.
The range for each design variable and the associated units are shown in Table~\ref{tab:dv_table}.
% We add the water recovery fraction only at the CRZ point as a design variable since we are optimizing $\dot{m}_{\rm{fuel,CRZ}}$.

@@

% [x] TODO: AL-PA, Define the T4 ratio with an equation and reference the equation in the table
% [x] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
% [x] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
% [x] TODO: PA-PA, explain variable ranges
\begin{table}[hbt!]
  \centering
  \caption{
    Multipoint optimization problem definition.
    The objective function is the fuel flow rate at the cruise condition.
    The constraints are net thrust and engine diameter constraint at the design point, TOC.
  }
  \small
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{r l l r l}
    \toprule
                    & Variable/Function              & Description                                                              & Units          & Quantity \\
    \hline
    minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Fuel flow rate at CRZ                                                    & \si{lbm/s}     & 1        \\
                    &                                &                                                                          &                &          \\
    with respect to & $X_{\rm{H_2O,CRZ}}$            & Water recovery mass fraction at CRZ                                      & -              & 1        \\
                    & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                                                   & -              & 1        \\
                    & $\rm{PR}_{\rm{LPC,TOC}}$       & TOC low-pressure compressor pressure ratio                               & -              & 1        \\
                    & $\rm{OPR}_{\rm{TOC}}$          & TOC overall pressure ratio                                               & -              & 1        \\
                    & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                                & \si{\degree R} & 1        \\
                    & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation~\eqref{t4ratio})                  & -              & 1        \\
                    & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation~\eqref{eq:vratio}) & -              & 1        \\
    \cline{3-5}
                    &                                & Total                                                                    &                & 7        \\
                    &                                &                                                                          &                &          \\
    subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                                 & \si{lbf}       & 1        \\
                    & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                     & \si{inch^2}    & 1        \\
    \cline{3-5}
                    &                                & Total                                                                    &                & 2        \\
    \bottomrule
  \end{tabular}
  \label{tab:opt_problem}
\end{table}

@@

% Thrust splits
% [x] TODO: PA-PA: Add thrust splits for each opt
% [x] TODO: AL-PA: I think this should be showing gross thrust from the fan divided by gross thrust from the core.
%                  The idea here is to show percentages of thrust generated by fan/core and how that changes with water recovery.
% \begin{table}[hbt!]
%   \centering
%   \caption{Thrust breakdown for each flight operating condition.
%     The net thrust, gross thrust, and ram drag are shown for each optimization result.
%   }
%   \small
%   \renewcommand{\arraystretch}{1.2}
%   \begin{tabular}{r l l l l l}
%     Point & Thrust Fraction & Jet-A Dry & Jet-A Wet & H2 Dry  & H2 Wet  \\
%     \toprule
%     TOC   & Core            & 6.47\%    & 6.05\%    & 5.95\%  & 5.47\%  \\
%           & Bypass          & 93.53\%   & 93.95\%   & 94.05\% & 94.53\% \\
%     \hline
%     RTO   & Core            & 6.31\%    & 5.87\%    & 5.77\%  & 5.26\%  \\
%           & Bypass          & 93.69\%   & 94.13\%   & 94.23\% & 94.74\% \\
%     \hline
%     SLS   & Core            & 6.11\%    & 5.68\%    & 5.58\%  & 5.09\%  \\
%           & Bypass          & 93.89\%   & 94.32\%   & 94.42\% & 94.91\% \\
%     \hline
%     CRZ   & Core            & 6.02\%    & 5.42\%    & 5.53\%  & 4.71\%  \\
%           & Bypass          & 93.98\%   & 94.58\%   & 94.47\% & 95.29\% \\
%     \bottomrule
%   \end{tabular}
%   \label{tab:thrust}
% \end{table}

@@

The TSEC improvement at CRZ due to water recovery for both fuels is shown on a bar chart in Figure~\ref{fig:barchart}.
Water recovery improves the TSEC approximately 5\% for both Jet-A and hydrogen fueled cycles.
% We see an improvement greater than 5\% at CRZ for TSEC for both fuels.
% [x] TODO: AL-PA, This is a good point, but maybe combine with the paragraph after the figure?
Most of the design variables for the optimal designs with and without water recovery vary only slightly for both fuels.
This suggests that the water recovery system accounts for a majority of the efficiency improvements.
Achieving a 5\% reduction in TSEC represents a large fuel savings over the lifecycle of an engine.
% This level of improvement would have a significant reduction in fuel costs over the course of an engine's lifecycle.
% [x] TODO: AL-PA, Add a sentence that introduces this citation and paraphrases the claim.  Then relate it to your findings.
As~\citeauthor{Strom2002} point out, a hydrogen-fueled engine would have close to 3 times more water in the exhaust than a similar Jet-A fueled counterpart.
% [x] TODO: AL-PA, I think we need to add some numbers here for the mass flow rate of water for jet-a and hydrogen to help this claim.
The engine designs with water recovery showed that there was about 2.38 \si{lbm/s} and 1.08 \si{lbm/s} of water in the core stream for \ce{H2} and Jet-A, respectively.
% Therefore, \ce{H2} is a much more appealing fuel to use with the proposed closed-loop water recovery system.
Hydrogen combustion offers an immediate reduction in emissions and produces more water in the exhaust stream.
With an advanced water recovery system, we can achieve better TSEC with hydrogen fuel than a standard Jet-A engine without water recovery.
To make hydrogen fueled engines a reality, we need to take advantage of the additional benefits of hydrogen combustion.
\subsection{Condenser Design Space Study}
\label{sub:dpqp_sweep}
% [x] TODO: AL-PA, I would emphasize that we did this sweep to explore the design space following our optimization results.
%                  Might be worth moving this into a new subsection.
% [x] TODO: AL-PA, This study wasn't motivated by a lack of literature, we want to explore the potential design space for the technology we just proposed and analyzed.
The efficiency improvement gained from water recirculation warrant a design space study for potential condenser technology.
Companies that are developing engines with water recirculation suggest that hydrogen can be used to as the heat sink for a water condenser~\cite{arpa-e_2021}.
We consider a condenser designed to fit inside the exhaust stream of a hydrogen-fueled turbofan engine.
The trade space for a condenser in the exhaust stream depends on the pressure loss and water recovery capability.
% A low pressure loss condenser would need to be developed for the water recirculation loop to be implemented.
% [x] TODO: AL-PA, dPqP is the relative total pressure loss not just a "pressure loss"

### 2023-05-10 figures/N3_cycle.tex
added presentation file
Intro and tables fixed

    % Create station labels
    % \node [station_label, below=8em of inlet.west] (1) {1};
    \node [station_label, below=6em of fan.west] (1) {1};
    % \node [station_label, below=8em of splitter.west] (13) {13};
    \node [station_label, below=6em of lpc.west] (2) {2};
    \node [station_label, below=6em of hpc.west] (25) {25};
    \node [station_label, below=6em of burner.west] (3) {3};
    \node [station_label, below=6em of hpt.west] (4) {4};
    \node [station_label, below=6em of lpt.west] (45) {45};
    \node [station_label, below=6em of corenozzle.west] (5) {5};
    \node [station_label, below=6em of bypnozzle.west] (17) {17};

@@

    % Draw station label connections
    % \path [line] (inlet.west) -- (1.north);
    \path [line] (fan.west) -- (1.north);
    % \path [line] (splitter.west) -- (13.north);
    \path [line] (lpc.west) -- (2.north);
    \path [line] (hpc.west) -- (25.north);
    \path [line] (burner.west) -- (3.north);
    \path [line] (hpt.west) -- (4.north);
    \path [line] (lpt.west) -- (45.north);
    \path [line] (corenozzle.west) -- (5.north);
    \path [line] (bypnozzle.west) -- (17.north);

>>>>

    % Create station labels
    \node [station_label, below=6em of inlet.west] (1) {1};
    \node [station_label, below=6em of fan.west] (12) {12};
    \node [station_label, below=6em of splitter.west] (13) {13};
    \node [station_label, below=6em of lpc.west] (2) {2};
    \node [station_label, below=6em of hpc.west] (25) {25};
    \node [station_label, below=6em of burner.west] (3) {3};
    \node [station_label, below=6em of hpt.west] (4) {4};
    \node [station_label, below=6em of lpt.west] (45) {45};
    \node [station_label, below=6em of corenozzle.west] (5) {5};
    \node [station_label, below=6em of bypduct.west] (17) {17};
    \node [station_label, below=6em of bypnozzle.west] (18) {18};

@@

    % Draw station label connections
    \path [line] (inlet.west) -- (1.north);
    \path [line] (fan.west) -- (12.north);
    \path [line] (splitter.west) -- (13.north);
    \path [line] (lpc.west) -- (2.north);
    \path [line] (hpc.west) -- (25.north);
    \path [line] (burner.west) -- (3.north);
    \path [line] (hpt.west) -- (4.north);
    \path [line] (lpt.west) -- (45.north);
    \path [line] (corenozzle.west) -- (5.north);
    \path [line] (bypduct.west) -- (17.north);
    \path [line] (bypnozzle.west) -- (18.north);
